\huge A Usability Evaluation of Tor Launcher

### 2017-03-15 pets2017-paper/pets2017-paper.tex
De-ligature my email address.
I learned the hard way on another paper that for some people,
copy-pasting from the PDF causes them to send mail to the nonexistent
address "ﬁﬁeld@cs.berkeley.edu" (where the "fi" are replaced with a
Unicode "ﬁ" ligature).
Add comma in "University of California Berkeley".

  \affil[1]{University of California Berkeley, E-mail: \mbox{lnl@cs.berkeley.edu}}

  \affil[2]{University of California Berkeley, E-mail: \mbox{fifield@cs.berkeley.edu}}

  \affil[3]{University of California Berkeley, E-mail: \mbox{nmalkin@cs.berkeley.edu}}

  \affil[4]{University of California Berkeley, E-mail: \mbox{ganesh.v@berkeley.edu}}

  \affil[5]{University of California Berkeley and International Computer Science Institute, E-mail: \mbox{egelman@cs.berkeley.edu}}

  \affil[6]{University of California Berkeley, E-mail: \mbox{daw@cs.berkeley.edu}}

>>>>

  \affil[1]{University of California, Berkeley, E-mail: \mbox{lnl@cs.berkeley.edu}}

  \affil[2]{University of California, Berkeley, E-mail: \mbox{f{}if{}ield@cs.berkeley.edu}}

  \affil[3]{University of California, Berkeley, E-mail: \mbox{nmalkin@cs.berkeley.edu}}

  \affil[4]{University of California, Berkeley, E-mail: \mbox{ganesh.v@berkeley.edu}}

  \affil[5]{University of California, Berkeley and International Computer Science Institute, E-mail: \mbox{egelman@cs.berkeley.edu}}

  \affil[6]{University of California, Berkeley, E-mail: \mbox{daw@cs.berkeley.edu}}
